Appendix A

### 2020-10-05 appendixA/appendixA.Rmd
included AIC in both parameter plots, and also the table.

```{r}
prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms
```

@@

model_comp_IC %>% 
  dplyr::select(data, dist, BIC) %>% 
  group_by(data) %>% 
  mutate(delta_within = signif(BIC - min(BIC), digits = 2)) %>% 
  ungroup() %>% 
  mutate(delta_across = signif(BIC - min(BIC), digits = 2)) %>% 
  dplyr::select(., -data)-> data_gt

@@

gt_tbl %>% 
  tab_header(
    title = md("**BIC comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  cols_label(
    delta_within = html("&Delta; BIC<sub>within</sub>"),
    delta_across = html("&Delta; BIC<sub>across</sub>")
  )

@@

```{r fig.height=10, fig.width=8}

plot_params <- function(prm_data){

@@

  prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    #facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "", subtitle = title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, color = prm_data$best_col))
}

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params() +
  #theme(axis.text.x = element_blank()) +
  NULL-> p1

nice_prms %>% 
  filter(., dist == "Gamma" & param == "SHAPE") %>% 
  plot_params() +
  #theme(axis.text.x = element_blank()) +
  NULL -> p2

nice_prms %>% 
  filter(., dist == "Gamma" & param == "RATE") %>% 
  plot_params() +
  #theme(axis.text.x = element_blank()) +
  NULL -> p3

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SHAPE") %>% 
  plot_params() +
  #theme(axis.text.x = element_blank()) +
  NULL-> p4

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SCALE") %>% 
  plot_params() +
  #theme(axis.text.x = element_blank()) +
  NULL-> p5

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
  plot_params() -> p6

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
  plot_params() ->p7

plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v")

>>>>

```{r}
prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black"))-> nice_prms
```

@@

model_comp_IC %>% 
  dplyr::select(data, dist, BIC, AIC) %>% 
  group_by(data) %>% 
  mutate(delta_BIC_within = signif(BIC - min(BIC), digits = 2),
         delta_AIC_within = signif(AIC - min(AIC), digits = 2)) %>% 
  ungroup() %>% 
  mutate(delta_BIC_across = signif(BIC - min(BIC), digits = 2),
         delta_AIC_across = signif(AIC - min(AIC), digits = 2)) %>% 
  dplyr::select(., -data) %>% 
  dplyr::select(dist, BIC, delta_BIC_within, delta_BIC_across, AIC, delta_AIC_within, delta_AIC_across)-> data_gt

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
  ) %>% 
  tab_spanner(
    label = md("**AIC**"),
    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
  ) %>% 
  cols_label(
    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
  )

@@

plot_params <- function(prm_data, best_col){

@@

  if(best_col == "BIC"){
    prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    #facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "", subtitle = title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
  }

  if(best_col == "AIC"){
    prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    #facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "", subtitle = title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
  }
  return(plot)

```{r fig.height=10, fig.width=12}

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p1

nice_prms %>% 
  filter(., dist == "Gamma" & param == "SHAPE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p2

nice_prms %>% 
  filter(., dist == "Gamma" & param == "RATE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p3

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SHAPE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p4

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SCALE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p5

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
  plot_params(., best_col = "BIC") -> p6

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
  plot_params(., best_col = "BIC") ->p7

plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p1

nice_prms %>% 
  filter(., dist == "Gamma" & param == "SHAPE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p2

nice_prms %>% 
  filter(., dist == "Gamma" & param == "RATE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p3

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SHAPE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p4

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SCALE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p5

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
  plot_params(., best_col = "AIC") -> p6

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
  plot_params(., best_col = "AIC") ->p7

plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid

plot_grid(bic_grid, aic_grid, ncol = 2)
